Highlighting Disputed Claims on the Web

### 2009-10-26 papers/www_disputefinder/disputefinder.tex
Finished my pass over the system section

\title{Highlighting Disputed Information on the Web}

@@

A user can install Disute Finder as an extension to the Firefox\footnote{http://www.mozilla.org/firefox} web browser. When installed Dispute Finder will highlight snippets of text that make disputed claims (Figure~\ref{highlight}). 
If a user clicks on a highlighted snippet, Dispute Finder will show articles that put forward different points of view,  each of which is from a source we believe the user is likely to trust (Figure~\ref{claimview}).

@@

\begin{description}
\item[What is disputed?] To be useful, the set of known disputed claims needs to be both large (so a user is likely to see snippets highlighted reasonably often) and accurate (so users aren't distracted by things that they would not consider to be disputed). We currently use a combination of crowdsourcing from users, and mining web sites such as Snopes and Politifact that already maintain lists of disputed claims. More generally, the challenge is not to determine if a claim is disputed by {\it anyone} but to determine whether there is an alternative point of view that this particular user would take seriously.

@@

Given a web page that the user is browsing, and a database of claims that we believe are disputed, how can we determine what snippets on the page are making claims that are in our database? We implemented and tested four approaches:

@@

\begin{figure}[tb]
	\begin{center}
	\includegraphics[width=7cm]{pictures/training.png}
	\caption{Bulk page marking}
	\label{training}
	\end{center}
\end{figure}

\begin{description}
\item[Explicit page marking:] If the page a user is reading contains a snippet that makes a disputed claim, the user can mark that snippet by selecting it, right clicking, and selecting "mark as disputed" from a popup menu.

\item[Bulk page marking:] The user enters a paraphrase of the claim into a web UI. The server searches the web for snippets that resemble this phrase using Yahoo BOSS~\cite{boss?} and shows the user the snippets it found. The user clicks on all of the snippets that they would like to mark.

\item[Server-side classification:] The server uses the examples from the bulk page marking interface to train a classifier. We used a simple baysian classifier with n-grams as its features. As the user gives examples of snippets that do or do not entail the original claim, the classifier learns what n-grams should or should not be in a snippet. Once the classifier is sufficiently trained, the server applies it to the rest of the results from Yahoo BOSS to automatically mark web pages. We have only partially implemented this approach.

@@

\item[Client-side entailment:] The browser extension runs a simple textual entailment algorithm over all sentences on every web page the user browse, checking to see if any sentence on the page entails any claim in the database. A user can enter additional paraphrases of a claim to help the entailment algorithm. This is the implementation used by the currently released version of Dispute Finder.
\end{description}

Explicit page marking has the highest accuracy, but the poorest coverage. Since a user is looking at the page in its entirity, they can read the snippet in context and make a good judgement about whether the snippet is indeed making the claim. However the manual effort required per page makes it difficult for this approach to scale. It can also be hard to motivate a user to mark snippets if it is unlikely that another user with the Dispute Finder extension will read exactly this page. This is the same problem that has hindered the adoption of web page annotation tools.

@@

Server side classification trades off more accuracy for more coverage. The classifier can mark more pages than a user could ever mark manually, but is inevitably less accurate than a human.

@@

The client side entailment method uses the standard Local Lexical Matching algorithm that is a common baseline in NLP. It divides the page into sentences, strips out stopwords, does stemming, and then looks for sentences that contain the keywords contained in a paraphrase of a known claim. If the claim contains a negation word (e.g. not, never, can't) then so must the matching sentence.

@@

The client side entailment method uses a simpler algorithm than the server-side classifier.

@@

Performing these tasks well is a hard problem, and we do not yet claim to have an implementation that is is good enough to be compelling for most users. We do however believe that Dispute Finder attacks an interseting problem that, if solved well, could significantly improve the utility of the web.

>>>>

\title{Highlighting Disputed Claims on the Web}

@@

A user can install Dispute Finder as an extension to the Firefox\footnote{http://www.mozilla.org/firefox} web browser. When installed Dispute Finder will highlight snippets of text that make disputed claims (Figure~\ref{highlight}). 
If a user clicks on a highlighted snippet, Dispute Finder will show articles that put forward different points of view,  each of which is from a source we believe the user is likely to trust (Figure~\ref{claimview}).

@@

\begin{description}
\item[What is disputed?] To be useful, the set of known disputed claims needs to be both large (so a user is likely to see snippets highlighted reasonably often) and accurate (so users are not distracted by things that they would not consider to be disputed). We currently use a combination of crowdsourcing from users, and mining web sites such as Snopes and Politifact that already maintain lists of disputed claims. More generally, the challenge is not to determine if a claim is disputed by {\it anyone} but to determine whether there is an alternative point of view that this particular user would take seriously.

@@

Given a web page, Dispute Finder needs to indentify which snippets are making known disputed claims. We implemented and tested four different approaches:

@@

\begin{figure}[tb]
	\begin{center}
	\includegraphics[width=7cm]{pictures/training2.png}
	\caption{Bulk page marking and server-side classification: classifier guesses are shown below the choice buttons}
	\label{training}
	\end{center}
\end{figure}

\begin{figure}[t]
	\begin{center}
	\includegraphics[width=7cm]{pictures/nlp_client_server2.png}
	\caption{Client-side entailment: the entailment algorithm runs on the client, using a claim database downloaded from the server}
	\label{nlp_client_server}
	\end{center}
\end{figure}

\begin{figure}[tb]
	\begin{center}
	\includegraphics[width=7cm]{pictures/paraphrases.png}
	\caption{Users can enter paraphrases of a claim to help the entailment algorithm}
	\label{paraphrases}
	\end{center}
\end{figure}

\begin{description}
\item[Explicit page marking:] The user explicitly marks a snippet on a page by selecting the snippet, and selecting "mark as disputed" from a context menu (Figure~\ref{mark_disputed}).

\item[Bulk page marking:] The user uses a search interface to rapidly gather a large number of snippets that contain similar phrases, and then marks them in bulk. The server uses Yahoo BOSS\footnote{http://developer.yahoo.com/search/boss} to search the web for snippets that resemble a paraphrase entered by the user. The user then selects all the snippets that they would like to mark (Figure~\ref{training}).

\item[Server-side classification:] The server uses the examples from the bulk page marking interface to train a classifier. We used a simple baysian classifier with n-grams as features. This classifier looks at the positive and negative examples given by the user and learns n-grams that should or should not be present in a snippet in order for it to make the claim.  Once the classifier has been trained, the server uses it to automatically choose which of the rest of the results from Yahoo BOSS should be marked (Figure~\ref{training}).

%We have only partially implemented this approach.
\todo{Should we say that we didn't completely finish this version?}

@@

\item[Client-side entailment:] The browser extension runs a simple textual entailment algorithm over all sentences on every web page the user browse, checking to see if any sentence on the page entails any claim in the database (Figure~\ref{nlp_client_server}). A user can enter additional paraphrases of a claim to help the entailment algorithm. This is the implementation used by the currently released version of Dispute Finder (Figure~\ref{paraphrases}).
\end{description}

Explicit page marking has the highest accuracy, but the poorest coverage. Since a user is looking at the page in its entirity, they can read the snippet in context and make a good judgement about whether the snippet is indeed making the claim. However the manual effort required per page makes it difficult for this approach to scale. We also foundf that it can also be hard to motivate a user to mark snippets if it is unlikely that another user with the Dispute Finder extension will read exactly this page. This same problem that has hindered the adoption of numerous web page annotation tools.

@@

Server side classification trades off more accuracy for more coverage. The classifier can mark more pages than a user could ever mark manually, and can keep marking new pages as they appear, but it is inevitably less accurate than a human.

@@

A further advantage of the client-side approach is that it avoids the need for the client to give the server any information about what pages the user is browsing. The list of all URLs and snippets that make disputed claims is too large and updates too frequently for it to be pratical for the client to store it locally, so the client instead asks the server for information about each URL the user browses, reducing user privacy. By contrast, the list of paraphrases is small enough and changes slowly enough that the client can maintain its own local copy of the database, removing the need for the client to tell the server what pages the user is browsing.

The client side entailment method uses the standard Local Lexical Matching (LLM) algorithm that is a common baseline in NLP. It divides the page into sentences, strips out stopwords, does stemming, and then looks for sentences that contain the keywords contained in a paraphrase of a known claim. If the claim contains a negation word (e.g. not, never, can't) then so must the matching sentence. To improve performance, rather than always running the LLM algorithm on every sentence on every page the user browses, the client starts by quickly scaccing the page for "hot terms" such as "Global Warming" that are known to appear in disputed claims. The hot terms are selected such that every claim contains at least one hot term. If a hot term is found, then the sentence that contained the hot term compared against all claims about that hot term.

\todo{Mention that we could add the +ve and -ve n-grams to the client code? Actually do this?}

@@

@@

Performing these tasks well is a hard problem, and we do not yet claim to have an implementation that is is good enough to be compelling for most users. We do however believe that Dispute Finder attacks an interesting problem that, if solved well, could significantly improve the utility of the web.

At the time of writing 11,682 people have installed and tried out Dispute Finder, 2,297 are active daily users, 140 have added new claims to our database, 149 have added articles, and our database contains 2,146 disputed claims.

\todo{Add count of disputed claims}
